Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-27 Scripts/Initial_Analysis.Rmd
Fixed figure 3 labels and LM

#### Project's Library
packages <- c(
  "dbemImport",
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt", # for estimating distances between points
  "viridis",
  "cowplot",
  "rfishbase"
)

@@

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List_emer,"_emergence.txt",sep="")

@@

# Time of Emergence of SST using methods here
Toe_sst <-fread(paste(my_path("D"),"Climate/ToE_sst.csv", sep ="")) %>% 
  clean_names()

@@

Eez_biogeo <- EEZ_CellID %>% 
  left_join(Biogeo_reg,
       by = "index") %>% 
  # Deal with NaNs in data
  mutate(biome = ifelse(biome == "NaN",0,biome)) %>% 
  filter(biome > 0) %>% 
  # Get frequency of biome per index
  group_by(eezid,basin,biome) %>% 
  summarise(nbiom=n(),
            nbasin=n()) %>% 
  # Select the more frequent biome per eez
  group_by(eezid,basin) %>% 
  top_n(1,nbiom) %>% 
  group_by(eezid,biome) %>% 
  top_n(1,nbasin) %>% 
  ungroup() %>% 
  select(-nbiom,-nbasin)

@@

Catch_trend <- my_path("D","Species","Catch_trend.csv", read = T) %>% 
  clean_names() %>% 
  filter(taxon_key %in% Taxon_list_emer) %>% 
  rename(sau_fishing_entity = territory) %>% 
  left_join(fishing_names,
            by = "sau_fishing_entity") %>% 
  filter(status != "No Trend") %>% 
  mutate(category = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
                         ifelse(status == "Max Exploited","Category B",
                                ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
                         )
         )
  )

@@

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
  ) %>% 
  rename(sf_eez_name=eez_name) %>% 
  left_join(Matching_names,
            by=  "sf_eez_name") %>% 
  clean_names() %>% 
  rename(eezid = eez_id)

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid_eck,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid_eck,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  # st_sfc(crs = 4326) %>%
  st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  # mutate(geometry = (geometry + c(18000000,9000000)) %% c(360) - c(18000000,9000000)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES"), quiet = TRUE) %>%
  # sf::st_sf(crs = 4326)
  sf::st_sf(crs = "+proj=eck4") # for tbular plot

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
  geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
  geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
             aes(start_lon,
                 start_lat,
                 col = per_plot),
             size = 0.05,
             col = "gray30",
             shape = 20,
             stroke = 1.5) +
  geom_path(data = subset(paths, time_step == time & per_plot > 0),
            aes(X, Y,
                group = interaction(line_id,subline_id),
                col = per_plot
            ),
            size = 0.3,
            arrow = arrow(length = unit(0.008, "npc"),
                          ends = "first"),
            show.legend = NA) +
  my_ggtheme_m() +
  scale_colour_viridis(
    name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    # option="magma",
    # direction = -1
  ) +
  scale_fill_viridis(
    name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
    limits = c(0,max(Map_data$per_plot)),
    breaks = seq(0,max(Map_data$per_plot),10),
    alpha = 0.8
    # option="magma",
    # direction = -1
  ) +
  ggsave("./Figures/fig2ax.png",
  width = 12,
  height = 8,
  units = "in"
  )

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis(
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = seq(2100,2000,-25),
      direction = -1
    ) +
    my_ggtheme_m() +
    ggsave(name_save,
           width = 12,
           height = 10,
           units = "in"
    )

@@

### Can we explain the ToE?

@@

Lm_data <- Eme_Res %>% 
  filter(tresh == "Tresh_one") %>% 
  left_join(Spp_depth) %>% 
  select(taxon_key,tresh,sf_eez_name,sau_fishing_entity,fishing_entity_id,emerging_yr,eezid,dem_pel) %>% 
  left_join(Toe_sst,
            by = c("eezid","tresh")
            ) %>% 
  left_join(Catch_trend,
            by = c("taxon_key","sau_fishing_entity","fishing_entity_id")
            ) %>% 
  left_join(Eez_biogeo,
            by = "eezid") %>% 
  left_join(Spp_env_pref,
            by = "taxon_key") %>% 
  left_join(Eez_centroids,
            by = "eezid") %>% 
  mutate(latitude = abs(latitude)) %>% 
  filter(tresh == "Tresh_one") %>% 
  distinct()

@@

# Model 1; all variables
M_all_var <- lm(emerging_yr ~ sst_toe + status + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 2; non demPel
M2 <- lm(emerging_yr ~ sst_toe + status + biome + dem_pel, data = Lm_data)

@@

# Model 3; non biome
M3 <- lm(emerging_yr ~ sst_toe + status + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 4; non status
M4 <- lm(emerging_yr ~ sst_toe + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 5; non sst
M5 <- lm(emerging_yr ~ status + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 6; all + basin
M6 <- lm(emerging_yr ~ sst_toe + status + biome + basin + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 7; Categories instead of status
M7 <- lm(emerging_yr ~ sst_toe + category + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 8; All variables + ccentroid lat
M8 <- lm(emerging_yr ~ sst_toe + category + biome + dem_pel + DemersPelag + latitude, data = Lm_data)

@@

tibble(
  "model" = c("all variables", "no demPel","no biome","no status","no sst","all + basin","Categories","lat centroids"),
  "AIC" = c(all_aic,M2_aic,M3_aic,M4_aic,M5_aic,M6_aic,M7_aic,M8_aic),
  "rsquared" = c(all_r,M2_r,M3_r,M4_r,M5_r,M6_r,M7_r,M8_r)
)

20282659

>>>>

#### Project's Library
packages <- c(
  "dbemImport",
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo", # for average mean
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt", # for estimating distances between points
  "viridis",
  "cowplot",
  "rfishbase",
  "stargazer" # For nice lm tables
)

@@

@@

# Temperature Time of Emergence
Toe_temp <- left_join(my_path("D","Climate", "ToE_sst.csv", read = T),
                      my_path("D","Climate", "ToE_bottemp.csv", read = T)
                      ) %>% 
  clean_names()

@@

Eez_biogeo <- EEZ_CellID %>% 
  # filter(eezid == 191) %>% 
  left_join(Biogeo_reg,
       by = "index") %>% 
  # Deal with NaNs in data
  mutate(biome = ifelse(biome == "NaN",0,biome)) %>% 
  filter(biome > 0) %>% 
  # Get frequency of biome per index
  group_by(eezid,biome) %>% 
  summarise(nbiom=n()) %>% 
  # Select the more frequent biome per eez
  group_by(eezid) %>% 
  top_n(1,nbiom) %>% 
  ungroup() %>% 
  select(-nbiom) %>% 
  distinct(eezid, .keep_all = T) # Croatia is 1/2. We arbritary allocated the first one

@@

Catch_trend <- my_path("D","Species","Catch_trend.csv", read = T) %>% 
  clean_names() %>% 
  filter(taxon_key %in% Taxon_list_emer) %>% 
  rename(sau_fishing_entity = territory) %>% 
  left_join(Fishing_names,
            by = "sau_fishing_entity") %>% 
  filter(status != "No Trend") %>% 
  mutate(category = ifelse(status %in% c("Developing","Rebuilding"),"Category A",
                         ifelse(status == "Max Exploited","Category B",
                                ifelse(status %in% c("Over Exploited","Collapsed","Category C"),"Category C", "No Category")
                         )
         )
  )

@@

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_list_emer,"_emergence.txt",sep="")

# Load all sp in one table
Eme_Res <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Neighbours,
            by = c("eez_name","eez_neighbour")
  ) %>% 
  rename(sf_eez_name=eez_name) %>% 
  left_join(Matching_names,
            by=  "sf_eez_name") %>% 
  clean_names()

@@

# Prepare data from results
Data <- Prop_results %>% 
  # get coords for sources
  left_join(Eez_centroid,
            by = "eez_name") %>%
  rename(source = eez_name,
         start_lon = longitude,
         start_lat = latitude,
         eez_name=eez_neighbour) %>% 
  # get coords for targets
  left_join(Eez_centroid,
            by = "eez_name") %>% 
  rename(target = eez_name,
         end_lon = longitude,
         end_lat = latitude) %>% 
  ungroup() %>% 
  # Plot miscs
  mutate(
    per_early = ifelse(is.na(per_early),0,per_early),
    per_mid = ifelse(is.na(per_mid),0,per_mid)
  ) %>% 
  drop_na() %>%
  filter(
    variable %in% c("mean_eez","n_spp")#,
    # source %in% c("Brazil","Argentina","Chile","Peru","Uruguay")
  )

# Convert to data to spatial
network_data_sf <- Data %>%
  select(start_lon, start_lat, end_lon, end_lat) %>% 
  purrr::transpose() %>% 
  purrr::map(~ matrix(flatten_dbl(.), nrow = 2, byrow = TRUE)) %>% 
  purrr::map(st_linestring) %>%
  st_sfc(crs = 4326) %>%
  # st_sfc(crs = "+proj=eck4") %>% # for tbular plot
  st_sf(geometry = .)%>%
  bind_cols(Data) %>%
  select(everything(), geometry) %>% 
  # Set circles ('cus the world is not flat!)
  st_segmentize(units::set_units(100, km)) %>% 
  mutate(geometry = (geometry + c(180,90)) %% c(360) - c(180,90)) %>%
  st_wrap_dateline(options = c("WRAPDATELINE=YES",  "DATELINEOFFSET=180"), quiet = TRUE) %>%
  sf::st_sf(crs = 4326)
  # sf::st_sf(crs = "+proj=eck4") # for tbular plot

@@

Prop_map <- ggplot() +
  geom_sf(data = subset(n_taxa_map, sovereignt != "Antarctica"),
          aes(fill = total_spp),
          size = 0.1,col = "white") +
geom_sf(data = World_eez_sf, size = 0.1, fill = "white", col = "gray30") +
geom_point(data = subset(Map_data, time_step == time & per_plot < 0),
           aes(start_lon,
               start_lat,
               col = per_plot),
           size = 0.05,
           col = "gray80",
           shape = 20,
           stroke = 1.5) +
geom_path(data = subset(paths, time_step == time & per_plot > 0),
          aes(X,
              Y,
              group = interaction(line_id,subline_id),
              col = per_plot
          ),
          size = 0.3,
          lineend = "round",
          arrow = arrow(length = unit(0.008, "npc"),
                        ends = "first"),
          show.legend = NA) +
  my_ggtheme_m() +
scale_colour_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # option="magma",
  # direction = -1
) +
scale_fill_viridis(
  name="Average Gain of Stock-Share Ratio (%)\nand Number of taxa (n)",
  limits = c(0,max(Map_data$per_plot)),
  breaks = seq(0,max(Map_data$per_plot),10)#,
  # alpha = 0.8
  # option="magma",
  # direction = -1
) +
ggsave("./Figures/fig2ax.png",
       width = 12,
       height = 8,
       units = "in"
)

@@

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text", 
             x =-130,
             y = -69,
             label = "Participation (USD)", 
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-73,-34,5,45,83),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-130,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-77,-37,3,42,82),
             y = -85,
             label = seq(2100,2000,-25), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -66, l = 250),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line"),
      axis.text = element_text(colour = "blue")
    ) +
    # guides(fill = guide_legend(nrow = 1))+
    ggsave(name_save,
           width = 12,
           height = 6,
           units = "in"
    )

@@

### Tab.1 Explain the ToE

@@

Lm_data <- Eme_Res %>% # 19728
  filter(tresh == "Tresh_one") %>% # 11490
  left_join(Spp_depth) %>% 
  select(taxon_key,tresh,sf_eez_name,sau_fishing_entity,fishing_entity_id,emerging_yr,eezid,dem_pel) %>% 
  left_join(Toe_temp,
            by = c("eezid","tresh")
            ) %>% 
  left_join(Catch_trend,
            by = c("taxon_key","sau_fishing_entity","fishing_entity_id")
            ) %>% # 11492
  left_join(Eez_biogeo,
            by = "eezid") %>% 
  left_join(Spp_env_pref,
            by = "taxon_key") %>% 
  left_join(Eez_centroids,
            by = "eezid") %>% 
  mutate(latitude = abs(latitude))

@@

# Model 1; all variables
M_all_var <- lm(emerging_yr ~ sst_toe + bot_toe + status + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 2; non demPel
M2 <- lm(emerging_yr ~ sst_toe + bot_toe + status + biome + dem_pel, data = Lm_data)

@@

# Model 3; non biome
M3 <- lm(emerging_yr ~ sst_toe + bot_toe + status + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 4; non status
M4 <- lm(emerging_yr ~ sst_toe + bot_toe + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 5; non sst
M5 <- lm(emerging_yr ~ status + bot_toe + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 6; all + basin
M6 <- lm(emerging_yr ~ sst_toe + bot_toe + status + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 7; Categories instead of status
M7 <- lm(emerging_yr ~ sst_toe + bot_toe + category + biome + dem_pel + DemersPelag, data = Lm_data)

@@

# Model 8; All variables + ccentroid lat
M8 <- lm(emerging_yr ~ sst_toe + bot_toe + category + biome + DemersPelag + latitude, data = Lm_data)

@@

tibble(
  "model" = paste("M",seq(1,8,1),sep=""),
  "AIC" = c(all_aic,M2_aic,M3_aic,M4_aic,M5_aic,M6_aic,M7_aic,M8_aic),
  "rsquared" = c(all_r,M2_r,M3_r,M4_r,M5_r,M6_r,M7_r,M8_r)
)

# UNIDAS 20282659

# The Winner is M8!

stargazer(M8, title = "Results", align=TRUE)
